Challenges and Solutions of Developing and Implementing a Revolutionary Novel Desktop-as-a-Service

### 2024-04-22 paper.tex
Some small additions in related work

Several works in literature have analyzed the latency of Cloud gaming services that have, in some aspects, similar requirements to DaaS offerings. For both cloud service categories, users expect a latency value that is not considered annoying when interacting with the service and its applications. Choy et al.~\cite{ChoyWongSimonRosenberg2012}, Claypool et al.~\cite{claypool2010latency}, and Jarschel et al.~\cite{jarschel2011evaluation} consider a maximum tolerable latency, based on subjective tests, being around 100\,ms. This relatively low value sets the demand for a fast network interaction between client and service and limits their maximum distance.

>>>>

Several works in literature have analyzed the latency of Cloud gaming services that have, in some aspects, similar requirements to DaaS offerings. For both cloud service categories, users expect a latency value that is not considered annoying when interacting with the service and its applications. Choy et al.~\cite{ChoyWongSimonRosenberg2012}, Claypool et al.~\cite{claypool2010latency}, and Jarschel et al.~\cite{jarschel2011evaluation} consider a maximum tolerable latency, based on subjective tests, being around 100\,ms. This relatively low value sets the demand for a fast network interaction between client and service and limits their maximum distance. As mentioned in Clincy et al.~\cite{clincy2013subjective}, The former cloud gaming service provider OnLive specified in the year 2010 that the distance between service provider and consumer should not be greater than 1000 miles (approx. 1600\,km) because otherwise the round-trip communications delay time between will be too long for video games.
